---
title: "Introduction to combcoint"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to combcoint}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(combcoint)
```

# Overview

The `combcoint` package implements the Bayer-Hanck [(2013)](https://doi.org/10.1111/j.1467-9892.2012.00814.x) Combining non-cointegration tests. A statistical approach that enhances the reliability of cointegration detection by aggregating the p-values from multiple individual cointegration tests into a single joint test statistic. Specifically, it integrates the results from the Engle-Granger (EG), Johansen (JH), Boswijk (BO), and Banerjee-Dolado-Mestre (BDM) tests using a Fisher-type combination method. This approach increases the power and robustness of cointegration testing, particularly in cases where the results of individual tests are mixed or inconclusive.

# 
